\documentclass[11pt, oneside]{article}  
\usepackage{geometry}                	
\geometry{a4paper}
\usepackage[parfill]{parskip}		
\usepackage{graphicx}	
\usepackage{pgfgantt}
\usepackage{pgfcalendar}	
\usepackage{pgfkeys}	
\usepackage{amssymb}
\usepackage{lscape}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\urlstyle{same} 

\title{COSC 345 Assignment 3} \author{Nathan Kennedy \texttt{1006384},
  Kat Lilly \texttt{8867318}, Tobyn Packer \texttt{5003352}, and
  \\Daniel Davidson \texttt{375621}} \date{\today}

\begin{document}

\maketitle
\tableofcontents
\newpage

\section{Beta Release}

Our app now contains three functioning games which can be opened via
speech commands from the main menu and controlled either by speech
commands or through touch. Two of the games (2048 and Frozen Bubble)
are open source games we have manipulated to work with voice commands
and Teragram is an original game, a maths practice game for children.

The application uses pocketSphinx to interpret speech commands:\linebreak
\href{https://github.com/cmusphinx/pocketsphinx}{https://github.com/cmusphinx/pocketsphinx}

\subsection{Since the Alpha}

We have made the following improvements and enhancements since our
alpha release:

\begin{itemize}
	\item The app no longer crashes on initial startup.
	\item Teragram is now able to be closed via speech command, at
          which point the main menu is reloaded.
	\item An open source implementation of the game 2048 has been
          added to the app and is now playable with speech commands.
	\item The open source game `Frozen Bubble' has been added to
          the app and voice controls implemented, however some
          debugging still needs to happen with respect to the speed of
          the launcher (see known issues for more).
        \item We have implemented an on/off switch for the speech
          recognition, so the games can be played with either voice
          control or touch screen control, with voice control being
          the default. This is currently working with Teragram and the
          main menu.
        \item We have implemented visual feedback for the speech
          recognition, currently working within Teragram. The user
          sees a `what I heard' message at the bottom of the screen,
          showing how the voice commands are being interpreted by the
          voice recognition software.
        \item In Teragram, we have replaced random multiplication
          questions with times tables practice. The user can change
          which times tables they are working on with the `too
          hard'/`too easy' buttons.
        \item In Teragram, we have added a powers of two multiple
          choice quiz. We chose to do this one as multiple choice
          rather than directly entering an answer so as to give the
          child practice at recognising powers of two - all the
          options in the quiz are whole powers of two.
\end{itemize}

\pagebreak

\section{Known Issues and Intended improvements}

\subsubsection*{Speech Recognition off-switch across all games}
We have successfully implemented the on/off switch in the main menu and 
Teragram but still have to implement it into 2048 and FrozenBubble.

\subsubsection*{Visual feedback across all games}
In Teragram, we have successfully implemented visual feedback which
informs the user of how voice inputs are being interpreted, but are
yet to implement it into the main menu, 2048 and FrozenBubble.


\subsubsection*{More robust number entry}
The current way of inputing numbers using speech is finicky and prone to
errors. We are unsure whether or not there is some easier way to do this,
but we would like to try different methods.


\subsubsection*{Frozen Bubble Launcher Speed}
Frozen Bubble is an open source game that is controlled strictly by touch. 
In order for a user to be hands-free, we have had to manipulate the code 
to have the launcher work with respect to time. This currently is working
but not in a functional fashion as it travels far too fast. The issue is 
that the launcher moves with respect to int values, however, for it to be 
functional we need decimals values. When trying to manipulate this it 
throws a chain of bugs where the values are used elsewhere in the game. 


\subsubsection*{Help Screen}

{\em remove this section? this may be implemented by the time we hand
  it in? if so add this stuff to 'since the alpha' section}

Without this documentation, a user would have no way of knowing
exactly what to say to the game to get it to do anything. Some kind of
pop-up display you could call at any moment displaying the voice
commands is neccessary.

\section{Testing}

\subsubsection*{Voice control}

Testing an application that is run by voice commands was not something
we felt could be done through automated methods without devoting a
large amount of time that could instead be spent implementing
features. Instead, frequent testing was done manually either through
emulators or by installing the apk on our own phones. We note that the
microphone on a typical phone is significantly better than the
microphone on a typical laptop or desktop computer, and so the app is
significantly easier to play on a phone than on an emulator.


\subsubsection*{Teragram}

For the Teragram game, we had extensive user testing performed by two
children, seven and four years old. In the months since the alpha
release, they have still been playing it frequently, so it has passed
the fun test and is clearly suitable for children of those ages, with
some room to grow, as some parts are too hard for them for
now. However, they do prefer to play it without using the voice
control. This is partly because they do not often find themselves in a
quiet enough place for the voice control to work reliably, but also
because they get frustrated that voice controls are a bit slower and
less reliable than entering answers via the touch screen.

\pagebreak

\section{User Documentation}

\subsection{Teragram}

The game starts up at level one, and the user can move to the easiest
level by tapping the `too hard' button or go up levels by tapping the
`too easy' button. Automatic leveling up happens when ten questions in
a row are answered correctly, or levelling down when you get two wrong
in a row. The user is not aware of the actual level, it's just that
questions get easier or harder - the bound on the random number
generator used in setting new questions is related to the level.

The game launches in addition mode, and the user can chose to move to
subtraction problems, or practice times tables or powers of two.

\subsection{2048}

2048 is a popular number name released on March 20, 2014. This game is
very simple; you can choose to slide the tiles up, down, left or right
by swipping the screen or saying `left', `right' `up' or `down'. Every
slide, all the digital squares will move to the direction of sliding
way. This is a really neat game, and there are many open source
implementations out there, but what makes it especially suitable for
our app is the simplicity of its controls - it's an interesting and
challenging game controlled with only four commands. Also there is no
time pressure in this game, so if it takes half a second for the
speech recogniser to work, this does not adversely affect the game
play.

\subsection{Frozen Bubble}
The aim of this game is to clear the screen by shooting the current
bubble in the launcher at its respective coloured bubbles on the
level. Saying `fire' or swipping up will shoot the bubble.

\subsection{Voice Controls}

You can control the game with the following voice commands:

\subsubsection{Main menu}

{\em is this still correct? do we have help menu coming from main page now?}

\begin{itemize}
  \item {\em\bf`game one'} - unsupported
  \item {\em\bf`Teragram' / 'game two'}  - this will take you to the game Teragram.
  \item {\em\bf`Twenty Fourty Eight' / 'game three'} - this will take you to the game 2048.
  \item {\em\bf`Frozen Bubble' / 'game four'} - this will take you to the game Frozen Bubble.
\end{itemize}

\subsubsection{Teragram}

{\em this needs updating}
\begin{itemize}
  \item {\em\bf`harder'} - Provides a harder question. 
  \item {\em\bf`easier'} - Provides an easier question.
  \item {\em\bf`new question'} - Provides a new question of the same type
  \item {\em\bf`addition'} -Provides an addition question
  \item {\em\bf`subtraction'} - Provides a subtraction question
  \item {\em\bf`multiplication'} - Provides a multiplication question 
  \item {\em\bf`number'} - Starts Number Input mode, see below
  \item {\em\bf`exit'} - Prompts a message confirming if they want to exit
 
\end{itemize}

\subsubsection{2048}

\begin{itemize}
	\item {\em\bf`left'} - All blocks will move to the left if possible. 
	\item {\em\bf`right'} - All blocks will move to the left if possible
	\item {\em\bf`up'} - All blocks will move to up if possible. 
	\item {\em\bf`down'} - All blocks will move to down if possible
	\item {\em\bf`exit'} - Prompts a message confirming if they want to exit
	
\end{itemize}

\subsubsection{Frozen Bubble}

\begin{itemize}
	\item {\em\bf`fire' or `now'} - Will fire the bubble
	\item {\em\bf`exit'} - Prompts a message confirming if they want to exit
	
\end{itemize}

\pagebreak

\subsubsection{Number Input}
\begin{itemize}
  \item {\em\bf numbers 0 to 9 inclusive} – Appends the spoken number
    to the end of your answer, ie. Speaking `one', `two' will give you
    12. Note that 0 is to be spoken `zero'
  \item {\em\bf `okay'} - Submits the current answer and exits Number
    Input mode
  \item {\em\bf `back'} - Removes the last number from your answer
  \item {\em\bf `clear'} - Removes the entirety of your answer
  \item {\em\bf `cancel'} - Exits Number Input mode
\end{itemize}

When entering numbers, please wait until the number you have just spoken appears
in the box before trying to input the next one.
Good Luck!

\section{Open Source components}

The code for the speech recognizer setup/permissions/asset copying is
taken almost directly from the pocketSphinx demo application here:
\url{https://github.com/cmusphinx/pocketsphinx-android-demo}

The phoneme definitions in our nktd.dic file are selectively taken
from the cmudict-en-us.dict file in that same demo.

The acoustic model we use is provided by CMUSphinx at
\href{https://sourceforge.net/projects/cmusphinx/files/Acoustic\%20and\%20Language\%20Models/US\%20English/}{sourceforge.net}

The game FrozenBubble taken from
\url{https://github.com/kthakore/frozen-bubble}

The game 2048 taken from
\url{https://github.com/BuddyBuild/2048-Android}
    


\end{document}
