\documentclass[11pt, oneside]{article}  
\usepackage{geometry}                	
\geometry{a4paper}                   			
\usepackage[parfill]{parskip}		
\usepackage{graphicx}	
\usepackage{pgfgantt}		
					
\usepackage{amssymb}

\title{COSC 345 Assignment 1}
\author{Nathan Kennedy, Kat Lilly, Tobyn Packer, Daniel Davidson}
\date{\today}							

\begin{document}
\maketitle

\section*{What we are going to build}

We intend to build an app containing a suite of games that can be
played without the use of one's hands. Entry to the app as well as
control of the games will all be voice controlled.

We will begin with a tetris game as a way to get started and learn all
the various things we'll need to learn, such as how to use the voice
to text software, how to write an android app, etc. This is a game
that has very simple keyboard inputs, so there shouldn't be
significant challenges beyond capturing the voice commands.

After this we intend to add one or more additional games. Hopefully
we'll come up with some ideas for games that are a bit more
interesting to control by voice than tetris, maybe something where the
gameplay is improved or changed by controlling it this way.

\subsection*{Intended users}

Our target users are anyone who does not have full use of their hands,
either permanently or temporarily. The app will be launched with the
voice control in the operating system, and the user will be able to
select a game and play it using only voice commands. 

Our intended users are defined not by a particular illness or injury or other source of disability, but only by this particular aspect of their interaction with a device, that is that that are unable to use their hands at this time.

\subsection*{Platforms}

We will build an Android app that runs on both smartphones and tablets, and possibly also on smart watches if one or more of the games we write is suitable for such a small screen.



\section*{How we will build it}

{\em I think in this section we should give each of us roles, we should talk about how we want to divide up the work. task oriented roles?}

{\bf Nathan} currently working on getting the app started

{\bf Kat} currently writing java tetris game (mostly from tutorials), using keyboard controls that will later be replaced with voice control.

{\bf Tobyn} something

{\bf Daniel} working with the voice recognition software 


\begin{ganttchart}{1}{12}
\gantttitle{2018}{12} \\
\gantttitlelist{1,...,12}{1} \\
\ganttgroup[progress=50]{Group 1}{1}{7} \\
\ganttbar{Task 1}{1}{2} \\
%\ganttbar{Task 1}\\
\ganttlinkedbar[progress=20]{Task 2}{3}{7} \ganttnewline
\ganttmilestone{Assignment 1 (report)}{7} \ganttnewline
\ganttbar{Final Task}{8}{12} \ganttnewline
\ganttmilestone{Assignment 2 (alpha release)}{7} \ganttnewline
\ganttlink{elem2}{elem3}
\ganttlink{elem3}{elem4}
\ganttlink{elem1}{elem3}
\end{ganttchart}


\section*{Timeline}

Things that need doing at the moment:
\begin{itemize}
\item Understanding the voice to text stuff - Daniel is working on
  this and will write a simple program that takes voice inputs and
  outputs them to screen or perhaps tries to match them to a list of
  game control commands
\item Figuring out how to get started writing an Android app - one of
  us should write a very simple app that starts up with a menu asking
  you to select which game to play
\item Getting the tetris.cpp code working in both windows and
  linux/osx, Kat and Tobyn working on this
\item Implementing tetris in Java - Kat is working on this
\item Understanding the voice controls that come with the Android
  operating system

  
\end{itemize}

\subsection*{Project timeline}

{\em Should insert a Gantt chart here}


\begin{table}[h!]
  \centering
  \begin{tabular}{|c|l|}
    \hline
    Date & Milestone\\
    \hline
    Friday 7th April & a working Java implementation of Tetris \\

    Friday 7th April & a bare bones nktd Android app that just has a
    menu of games \\

    Friday 7th April & have something that takes audio input from
    microphone and outputs text \\

    Monday 9th April & have gotten started with Android Studio and Gradle \\

    Monday 16th April & 1st report due \\

    Friday 4th May & set some goals to finish by this date \\

    Monday 28th May & 2nd assignment due - alpha release of nktd \\
    \hline
  \end{tabular}
\end{table}


%\subsection*{}



\end{document}  

